### 2021-02-24 architecture.tex
Shorten the loss formulas by using multline
Fix a double space due to iftoggle command

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following
\iftoggle{LONG}{
sections (see also \cref{fig:architecture}):
\begin{itemize}
\item \Cref{sec:graphifier}: The graph constructor transforms the input \gls{cnf} problem into a problem graph.
\item \Cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
\item \Cref{sec:output}: The output function extracts symbol costs from the symbol embeddings.
\item \Cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
\end{itemize}
}{
sections (see also \cref{fig:architecture}).
}

@@

Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}{P}$).
The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
or alternatively $S(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
% We have positive S score for correctly predicted examples.
% The loss function transorms that into a loss value close to 0.
We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018},
% p. 128
a loss function routinely used in classification tasks in \acrlong{ml}:
\begin{align*}
\loss(P, \PrecBetter, \PrecWorse)
&= - \log \sigmoid S(\PrecBetter, \PrecWorse) \\
&= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
&= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i)))
%&= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
\end{align*}
% FB: Note: I have included the full expansion to make it visible how the loss depends on $c$.
% To a skilled NN practitioner, it should now be obvious that the loss is differentiable w.r.t. $c$.
\todo{FB: Consider exposing the form with inverse precedences to single out the $c$ values and expose the $c$ gradient better.}

>>>>

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following\iftoggle{LONG}{
sections (see also \cref{fig:architecture}):
\begin{itemize}
\item \Cref{sec:graphifier}: The graph constructor transforms the input \gls{cnf} problem into a problem graph.
\item \Cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
\item \Cref{sec:output}: The output function extracts symbol costs from the symbol embeddings.
\item \Cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
\end{itemize}
}{
sections (see also \cref{fig:architecture}).
}

@@

Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}{P}$).
The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
or alternatively $S(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
% We have positive S score for correctly predicted examples.
% The loss function transorms that into a loss value close to 0.
We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018},
% p. 128
a loss function routinely used in classification tasks in \acrlong{ml}:
\begin{multline*}
\loss(P, \PrecBetter, \PrecWorse)
= - \log \sigmoid S(\PrecBetter, \PrecWorse)
= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i)))
%= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
\end{multline*}
% FB: Note: I have included the full expansion to make it visible how the loss depends on $c$.
% To a skilled NN practitioner, it should now be obvious that the loss is differentiable w.r.t. $c$.
\todo{FB: Consider exposing the form with inverse precedences to single out the $c$ values and expose the $c$ gradient better.}
